---
title: "Hand Calc Ranking Support"
author: "Steven"
date: '2022-10-14'
output: 
  html_document:
    toc: TRUE
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Libraries.R")

```

# Possible Cards

52 Cards going from 2 - A (13)\* 4 suits (4) .

Lets assign values to each number where higher numbers = betteir

```{r building deck}

Card_Values <- data.frame(cbind(c(2,3,4,5,6,7,8,9,10,"J","Q","K","A"),c(1:13))) %>% 
  rename(., Value = X2, Number = X1) %>% 
  mutate(., Value = as.numeric(Value))

Suits<-c("S","H","D","C") #Spade, Hearts, Diamond, Clubs

Deck <-
  cross2(Card_Values$Number, Suits) %>% 
  sapply(., rbind) %>%  
  as_tibble()

DeckC <- map(Deck, 1) %>% unlist
DeckS <- map(Deck, 2) %>% unlist

Deck <- tibble(Number = DeckC, Suit = DeckS, Card = paste(DeckC, DeckS, sep = ""))  %>% left_join(., Card_Values, by = c("Number" = "Number"))
attributes(Deck$Number) <- NULL
attributes(Deck$Suit) <- NULL

rm(DeckC, DeckS)

print(Deck)

```

# Hand Score Evaluation

Calculate the absolute probabilities of each hand. Should follow
[wiki](https://en.wikipedia.org/wiki/Poker_probability). For texas
holdem - I think we only need to care about the 7 card sample space. I
think it'll make sense to just scrape the web for the raw frequencies of
each hand. 5 and 7 cards... I don't think we need to worry about 6 card
frequency since we always will end at 7 cards anyways. Below is the web
scrape which we will only need to run once, and then we can code out by
checking if the frequency table exists otherwise run code and just save
the data.

```{r wiki probability table scrape}

if(!exists("FiveCardFrequency")){
  
wiki = "https://en.wikipedia.org/wiki/Poker_probability"

paths_allowed(paths = wiki)

tables <- read_html(wiki) %>% html_elements("table") %>% html_table() # Might need to find where the table are if they move

FiveCardFrequency <- tables[[1]]
SevenCardFrequency <- tables[[2]]

FiveCardFrequency[,-7]
SevenCardFrequency[,-6]
}


```

# Hand Picker

A script to identify the hand you have. We'll rely on the Holdem package
for dealing, simulation, and other aspects of texas holdem. We'll need
to convert between the holdem package and ours

```{r Hand Picker}

source("Hand Select.R")

d <- deal1(9)
Value <- c(d$plnum1[1,1], d$plnum1[1,2], d$brdnum1)-1
Suit <- c(d$plsuit1[1,1], d$plsuit1[1,2], d$brdsuit1)

 c(d$plnum1[1:nrow(d$plnum1),1], d$plnum1[1:nrow(d$plnum1),2], d$brdnum1)

```

Figuring out a way to have card_values \* combo = Total Value (TV).
Possible to update the offset term to the minimum of the prior hand.

Let n represent card value and c represent the minimum offset so that
each hand falls in the correct place above the hand below. In the
following we allow c to be $c^h$ where h represents the ranking of the
hand and c as 13. Possible other ideas are to take the log value or to
set c to the minimum of the prior hand max.

Will have to compare with the handeval function from the Holdem package.

**Top Card:** $$\text{TV} = n$$ $$\min (\text{TV}_\text{Top Card}) = 1$$
$$\max (\text{TV}_\text{Top Card}) = 13$$ **One Pair:**
$$\text{TV} =  2 \sum n + c$$ $$\min (\text{TV}_\text{Pair}) = 15$$
$$\max (\text{TV}_\text{Pair}) = 39$$ **Two Pair:** Note that A's with
2's beat K's with J's
$$\text{TV} = 3n_1 +0.25n_2 + c^2 \text{, where } n_1 > n_2$$
$$\min (\text{TV}_\text{Two Pair}) = 175.25$$
$$\max (\text{TV}_\text{Two Pair}) = 211$$ **Trips:**
$$\text{TV} = 3 \times \sum n + c^3$$
$$\min (\text{TV}_\text{Trips}) = 2200$$
$$\max (\text{TV}_\text{Trips}) = 2236$$ **Straight:**
$$\text{TV} = \sum_1^5 n_i + c^4 \text{, where n is consecutive} $$
$$\min (\text{TV}_\text{Straight}) = 28576$$
$$\max (\text{TV}_\text{Straight}) = 28616$$ **Flush:** Note that the
high card flush wins.
$$\text{TV} = \sum_1^5 (n_i \times w_i) + c^4 + \text{Flush Bonus} \text{, where \(w_i = \{x^2,x,x^0,x^{-1},x^{-2} \}\) and \(x \geq 12\) and \(n_{i+1} \geq n_i\)}$$
$$\min (\text{TV}_\text{Flush}) = 30458.09$$
$$\max (\text{TV}_\text{Flush}) = 30603.07$$ **Full House**
$$\text{TV} = w_1 \times n_1 + w_2 \times n_2 + c^5  \text{, where \(n_1\) had 3 cards and \(n_2\) has 2 and \(w_1 \geq 13 \times w_2\) }$$
$$\min (\text{TV}_\text{FH}) = 371308$$
$$\max (\text{TV}_\text{FH}) = 371474$$

**Four of a kind** $$\text{TV} = 4 \times n + c^6$$
$$\min (\text{TV}_\text{FH}) = 4826817$$
$$\max (\text{TV}_\text{FH}) = 4826861$$

**Straight Flush**
$$\text{TV} = \sum_1^5 n_i + c^6  + \text{Flush Bonus} \text{, where n is consecutive} $$
$$\min (\text{TV}_\text{FH}) = 4826824$$
$$\max (\text{TV}_\text{FH}) = 4826864$$

**Royal Flush** The same as straight flush so it doesn't need to be
coded.

**Residuals** To account for any kickers, since every hand has a max
value of 5 cards, there will be cases where there are no kickers

```{r call to TV function}

source("Total Hand value.R")

```

# Future Possible Hands

# Bets & Weight Modeler

# Ultimate Model

# Call, Bet or Fold

```{r}
```

```{r}
```
